---
title: "dogmarep"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dogmarep}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dogmarep)
```

# DogmaRep

**Group 01 package for lab08**

## Installation from GitHub

You can install the development version of dogmarep like so:

```{r}
#| messages : False
install.packages("devtools") 
devtools::install_github("https://github.com/rforbiodatascience25/group_01_package")
```

The package will install its dependencies as found in DESCRIPTION

## Example workflow

DogmaRep is able to compute an example conversion from DNA \> RNA \> peptide sequence, with the possibility of plotting the peptide sequence as well.

### Generating random nucleotide sequence

```{r}
DNA_seq <- generate_nucleotides(seq_size = 30)
```

### Converting from DNA to RNA

```{r}
RNA_seq <- dna_to_rna(DNA_seq)
```

### Split RNA into codons

```{r}
codons <- codon_splitter(RNA_seq)
```

### Translating codons to amino acids (peptide sequence)

```{r}
peptide_seq <- codon_to_letter(codons)
```

### Plotting peptide sequences

```{r}
AA_count_bar_plot(peptide_seq)
```
